Defficiency Screen Functional Analysis

### 2023-07-10 DeficiencyScreen/GO_Analysis.Rmd
update

library(biomaRt)
library(org.Dm.eg.db)
library(goseq)
library(GO.db)
library(visNetwork)
library(rrvgo)
library(plotly)
library(KEGGREST)
library(pathview)
##library(RColorBrewer)
```

```{r echo = F, include =F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT.EdgeR.Table.csv"),row.names = 1)
GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

##CamiData = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/Genes by Df Modifier.csv")

##background = setNames(unique(CamiData$Background), unique(CamiData$Background))

##moderate = setNames(rep(0, length(background)), names(background))

##moderate[unique(CamiData$Moderate)] = 1

##strong = setNames(rep(0, length(background)), names(background))

##strong[unique(CamiData$Strong)] = 1

##lethal = setNames(rep(0, length(background)), names(background))

##lethal[unique(CamiData$Lethal)] = 1

##enhancer = setNames(rep(0, length(background)), names(background))

##enhancer[unique(CamiData$Enhancers)] = 1

##no.effect = setNames(rep(0, length(background)), names(background))

##no.effect[unique(CamiData$No.Effect)] = 1

##FB2Ensembl
##x1=as.list(org.Dm.egENSEMBL2EG)
##Ensembl2Symbol
##x2=as.list(org.Dm.egSYMBOL)
##Symbol2Ensembl
##x3=as.list(org.Dm.egSYMBOL2EG)
##Ensembl2FB
##x4=as.list(org.Dm.egENSEMBL)
##ensembl to FBgn
##x5=as.list(org.Dm.egFLYBASE)

##FBgn2ensembl = row.names(CamiData)
##names(FBgn2ensembl) = row.names(CamiData)
##tempEG = unlist(x1[lengths(x1)==1][row.names(CamiData)])
##FBgn2ensembl[names(tempEG)]=tempEG

##ensembl2symbol = row.names(CamiData)
##names(ensembl2symbol) = FBgn2ensembl
##tempSymbol = unlist(x2[FBgn2ensembl])
##ensembl2symbol[names(tempSymbol)]=tempSymbol
##symbol2ensembl = names(ensembl2symbol)
##names(symbol2ensembl) = ensembl2symbol

##write.csv(names(symbol2ensembl)[grep("FBgn", names(symbol2ensembl))], "/Users/johncsantiago/Documents/CamiExtraGenes.csv")

##extras = read.csv("/Users/johncsantiago/Downloads/FlyBase_Symbol_download.csv", row.names = 1)
##ensembl2symbol[row.names(extras)] = extras$SYMBOL

##symbol = ensembl2symbol

##symbol = background

##symbol[intersect(GeneIDKey$FBgn, background)] = 
##  GeneIDKey[intersect(GeneIDKey$FBgn, background), "Symbol"]

##CamiData = data.frame(FBgn       = background[1:14674],
##                      Symbol     = symbol[1:14674],
##                      Moderate   = moderate[1:14674],
##                      Strong     = strong[1:14674],
##                      Lethal     = lethal[1:14674],
##                      Enhancer   = enhancer[1:14674],
##                      No.Effect  = no.effect[1:14674])

##write.csv(CamiData, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv")

Df.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv", row.names = 1)

@@

##write.csv(kegg.names, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv")
kegg.names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv", row.names = 1)

keggID=keggConv("dme","ncbi-geneid")

kegg = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/kegg.symbol2path.RData")

@@

Moderate.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateGOAnalysis.csv", row.names = 1)
Strong.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/StrongGOAnalysis.csv", row.names = 1)

Repress.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorGOAnalysis.csv", row.names = 1)
Lethal.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalGOAnalysis.csv", row.names = 1)
Enhance.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerGOAnalysis.csv", row.names = 1)

@@

GO.data = Moderate.GO
GO.data = GO.data[GO.data$ontology == 'BP',
                  c("category", "term","adjp", "numDEInCat", "numInCat")]

@@

@@

simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont="BP",
                                method="Rel")

##write.csv(simMatrix, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv")

reducedTerms <- reduceSimMatrix(simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")
##write.csv(reducedTerms,"/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv")

##simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
##reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)

@@

```{r, fig.align='left', include=F}

scatterPlot(simMatrix, reducedTerms)

@@

```{r, include=F, echo=F}
GO2Gene   = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GenesInGOTerms.csv", row.names = 1)

ccpar=as.list(GOCCPARENTS)
ccchild=as.list(GOCCCHILDREN)

bppar=as.list(GOBPPARENTS)
bpchild=as.list(GOBPCHILDREN)

mfpar=as.list(GOMFPARENTS)
mfchild=as.list(GOMFCHILDREN)
```

```{r, include=F, echo=F}

compare = "GRM.CxDf"
filter.samples = c("GR.M", "TktDfGR.M")

sigs = row.names(TKT.EdgeR)[TKT.EdgeR[,compare]<=.05]
sigs = sigs[apply(cpmdata[sigs,groups$Group %in% filter.samples], 1, min) > 10]

genes=c(rep(0, nrow(cpmdata)))
names(genes) = row.names(cpmdata)
genes[sigs] = 1
names(genes) = GeneIDKey[names(genes), "Symbol"]

pwf=nullp(genes,"dm3","geneSymbol")

GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category

GO.wall$Significant = "not"
GO.wall[GO.wall$adjp <= .05, "Significant"] = "sig"
sigGO = GO.wall[GO.wall$adjp<.05,]

##Biological Processes
bpGO = sigGO[sigGO$ontology == 'BP',]

##parent terms are those directly above in hierarchy
## isa implies a defining relationship; part of implies they contribute to the category

parents = bppar[bpGO$category]

parents = data.frame(from = unlist(parents),
                     label = substring(names(unlist(parents)),12),
                     to = substring(names(unlist(parents)),1,10))

parents = parents[parents$to %in% row.names(GO.wall),]

children = bpchild[bpGO$category]

children = data.frame(from = substring(names(unlist(children)),1,10),
                      label = substring(names(unlist(children)),12),
                      to = unlist(children))

children = children[children$to %in% row.names(GO.wall),]

edges = rbind(parents, children)
edges = edges[edges$label == "isa",]
edges = unique(edges)

edges = edges[GO.wall[edges$to, "numDEInCat"]>0,]

node.id = unique(c(edges$from, edges$to))
node.label = GO.wall[node.id, "term"]
node.group = GO.wall[node.id, "Significant"]
node.value = 100*(GO.wall[node.id, "numDEInCat"]/GO.wall[node.id, "numInCat"])

nodes = data.frame(id = node.id,
                   label = node.label,
                   group = node.group,
                   value = node.value)
```

```{r include=F}

visNetwork(nodes, edges)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-70),enabled=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows='to')%>%
  visGroups(groupname = "sig", shape = "box", color = list(background = "gold", border="black", groupname="black"),physics=F,font=list(color="black"))%>%
  visGroups(groupname = "not", shape = "dot", color = list(background = "grey", border="black", groupname="black"),physics=T,font=list(color="black"))

>>>>

##library(biomaRt)
##library(org.Dm.eg.db)
##library(goseq)
##library(GO.db)
##library(visNetwork)
library(rrvgo)
library(plotly)
##library(KEGGREST)
##library(pathview)
##library(RColorBrewer)
```

```{r echo = F, include =F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
Df.data = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
##kegg = readRDS(gzcon(url(paste0(git.dir,"DeficiencyScreen/DataFiles/kegg.symbol2path.RData"))))
##kegg.names = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/KEGG.names.csv"), row.names = 1)

Moderate.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/ModerateGOAnalysis.csv"), row.names = 1)
Strong.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/StrongGOAnalysis.csv"), row.names = 1)
Repress.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/RepressorGOAnalysis.csv"), row.names = 1)
Lethal.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/LethalGOAnalysis.csv"), row.names = 1)
Enhancer.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/EnhancerGOAnalysis.csv"), row.names = 1)

@@

@@

@@

```{r echo = F, include =F}

GO20 = function(GO.data, GO.ontology){
GO.data = GO.data[GO.data$ontology == GO.ontology,
                  c("category", "term","adjp", "numDEInCat", "numInCat")]

@@

  return(fig)
}

```{r echo = F, include =F}

GO.data = Repress.GO
GO.ontology = "BP"

GO.fig = GO20(GO.data, GO.ontology)

GO.fig

@@

simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont=GO.ontology,
                                method="Rel")

reducedTerms <- reduceSimMatrix(simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")

@@

@@

### 2023-07-10 DeficiencyScreen/KEGG_Analysis.Rmd
update

```{r echo = F, include =F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
Df.data = read.csv(paste0(git.dir,"GeneralDataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
Df.data$CG = GeneIDKey[row.names(Df.data),"CG"]
Df.data$Repress = 0
Df.data$Repress[Df.data$Moderate == 1|Df.data$Strong == 1] = 1
kegg = readRDS(gzcon(url(paste0(git.dir,"DeficiencyScreen/DataFiles/kegg.symbol2path.RData"))))
kegg.names = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/KEGG.names.csv"), row.names = 1)

@@

```{r fig.width=10}

@@

```{r echo = F}

>>>>

```{r echo = F, include =F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
Df.data = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
kegg = readRDS(gzcon(url(paste0(git.dir,"DeficiencyScreen/DataFiles/kegg.symbol2path.RData"))))
kegg.names = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/KEGG.names.csv"), row.names = 1)

@@

```{r echo = F, fig.width=10}

@@

```{r echo = F, fig.align='center'}
